Supplement 1: Different Response Distributions

### 2018-10-06 pkg/disttree/inst/draft/supplement/Rain_stationwise_results.Rnw
omit concordance
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2291 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 0c81e683da54475febf987bef6b3c53106d5c7bf
adapted to changes in variable importance barplot
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2309 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 535230c8ec202851f14de5ae50cac85c6cce076b

<<echo = FALSE, results=hide>>=
## station
station <- "_STATION_"
if(station == "SeeimPaznaun") station <- "See im Paznaun"
if(station == "MatreiinOsttirol") station <- "Matrei in Osttirol"
if(station == "LadisNeuegg") station <- "Ladis-Neuegg"
if(station == "StJohannimWalde") station <- "St.Johann im Walde"
if(station == "OchsengartenObergut") station <- "Ochsengarten-Obergut"

@@

<<varimp, fig=TRUE, echo=FALSE, height=4, width=6.4>>=
par(mar = c(5, 10, 1, 2))
barplot(varimp10, horiz = TRUE, las = 1, axes = FALSE,
        xlab = "Mean decrease in CRPS")
axis(1, at = seq(0, ceiling(max(varimp10) * 5)/5, 0.2), las = 1, mgp = c(0, 1, 0))
@

>>>>

<<echo = FALSE, results=hide>>=
## station
station <- "_STATION_"

if(station == "SeeimPaznaun") station <- "See im Paznaun"
if(station == "MatreiinOsttirol") station <- "Matrei in Osttirol"
if(station == "LadisNeuegg") station <- "Ladis-Neuegg"
if(station == "StJohannimWalde") station <- "St.Johann im Walde"
if(station == "OchsengartenObergut") station <- "Ochsengarten-Obergut"

@@

<<varimp, fig=TRUE, echo=FALSE, height=4, width=6.4>>=
par(mar = c(5, 10, 1, 2))
barplot(varimp10, horiz = TRUE, las = 1, axes = FALSE,
        xlab = "Mean increase in CRPS",
        xlim = c(0,0.09))
axis(1, at = seq(0, ceiling(max(varimp10) * 5)/5, 0.02), las = 1, mgp = c(0, 1, 0))
@
